\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2016-01-17 evaluation.tex
fix

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{0.3em}
\begin{tabular}{l rrrrr rr}
\centering
\input{experiments/tables/statistics.tex}
\end{tabular}
\caption{Statistics from modeling the environment of the three Microsoft MyCloud-based systems under test. The ($\star$) denotes ``awaiting confirmation''.}
\label{tab:stats}
\vspace{-3mm}
\end{table}

@@

Modeling Fabric required approximately five person months, an effort undertaken by the authors of \psharp. In contrast the other two systems discussed in this paper were modeled and tested by their corresponding developers. Although modeling Fabric required a significant amount of time, it is a one-time effort, which only needs incremental refinement with each release. Having modeled Fabric, we are now able to systematically test numerous services built on top of it.

>>>>

\newcommand{\colspacing}{\hspace{1.8em}}
\begin{table}[t]
\small
\centering
\setlength{\tabcolsep}{0.3em}
\begin{tabular}{l rrrrr rr}
\centering
\input{experiments/tables/statistics.tex}
\end{tabular}
\caption{Statistics from modeling the environment of the three Microsoft Azure-based systems under test. The ($\star$) denotes ``awaiting confirmation''.}
\label{tab:stats}
\vspace{-3mm}
\end{table}

@@

Modeling Fabric required approximately five person months, an effort undertaken by the authors of \psharp. In contrast the other two systems discussed in this paper were modeled and tested by their corresponding developers. Although modeling Fabric required a significant amount of time, it is a one-time effort, which only needs incremental refinement with each release.
